Data analytics effects in Baseball

### 2023-10-30 manuscription/manuscription.tex
method, result sections change

\section{Introduction}
\label{sec:intro}
Sport psychology, an interdisciplinary field integrating concepts from both psychology and sports science, has become a fundamental element in enhancing athletic performance across a spectrum of sports, baseball included.
Its primary focus is to comprehend and optimize the psychological components that affect an athlete's mindset, emotions, and conduct, ultimately aiming to elevate their performance.
Now, let's explore specific key domains within sport psychology that exert significant influence on baseball players.
Baseball was selected as the focal sport due to its comprehensive nature, allowing for an analysis of nearly every facet of the game, except for the mental readiness of the player upon entering the field. 
Previous studies in the field \citet{Dalmass2018baseball} have provided valuable insights, and we seek to build upon their findings.

@@

% roadmap
The rest of the paper is organized as follows.
The data will be presented in Section~\ref{sec:data}.
The methods are described in Section~\ref{sec:meth}.
The results are reported in Section~\ref{sec:resu}.
A discussion concludes in Section~\ref{sec:disc}.

@@

\section{Methods}
\label{sec:meth}
The study was designed as a two-sample experiment employing a differences-in-differences analysis approach.
Participants were categorized into three positional groups and further divided into either control or experimental groups. 
These results were evaluated as t-tests for differences in mean between groups.Method way\citep[e.g.,][]{Dalmass2018baseball}.

@@

@@

\bibliography{../manuscript/refs}
\bibliographystyle{chicago}

>>>>

\section{Introduction}
\label{sec:intro}
Sport psychology, an interdisciplinary field integrating concepts from both psychology and sports science, has become a fundamental element in enhancing athletic performance across a spectrum of sports, baseball included.
Its primary focus is to comprehend and optimize the psychological components that affect an athlete's mindset, emotions, and conduct, ultimately aiming to elevate their performance.
Now, let's explore specific key domains within sport psychology that exert significant influence on baseball players.
Baseball was selected as the focal sport due to its comprehensive nature, allowing for an analysis of nearly every facet of the game, except for the mental readiness of the player upon entering the field. 
Previous studies in the field \cite{Dalmass2018baseball} have provided valuable insights, and we seek to build upon their findings.

@@

% roadmap
The rest of the paper is organized as follows.\\
The data will be presented in Section~\ref{sec:data}.\\
The methods are described in Section~\ref{sec:meth}.\\
The results are reported in Section~\ref{sec:resu}.\\
A discussion concludes in Section~\ref{sec:disc}.\\

@@

We can see the number of players in each team in Figure~\ref{fig:team}.
\graphicspath{{images/}}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{baseball team.pdf}
  \caption{The number of players in each team in 2016 batting dataset}
  \label{fig:team}
\end{figure}

\section{Methods}
\label{sec:meth}
The research was structured as a two-sample experiment utilizing a differences-in-differences analysis method.
The participants were classified into three positional groups and then subdivided into either control or experimental groups. 
The outcomes were assessed using t-tests to analyze the differences in means between the groups.Method way\cite*{Dalmass2018baseball}.

@@

\begin{table}[tbp]
  \caption{The distribution of censored participants}
  \label{tab:rv}
\centering
\begin{tabular}{rrrr}
  \toprule
  Position & Assigned Group & Did Not Meet AB or IP & Did Not Play\\ 
  \midrule
Pitcher & Control & 3 & 1\\
Pitcher & Experiment & 2 & 1\\
Infield & Control & 1 & 0 \\
Infield & Experiment & 2 & 2\\
Outfield & Control & 1 & 0\\
Outfield & Experiment & 1 & 0\\
  \bottomrule
\end{tabular}
\end{table}

@@

\begin{thebibliography}{9}

  \bibliography{refs.bib}
  \bibliographystyle{chicago}
\end{thebibliography}
